Title

### 2024-03-12 outputs/paper/paper.qmd
paper updated

# read in data
file_path <- "../../outputs/data/filtered_data.csv"
filtered_data <- read_csv(file_path, show_col_types = FALSE)
```

@@

@@

>>>>

# read in data
file_path_0 <- "../../inputs/data/raw_data.csv"
file_path_1 <- "../../outputs/data/filtered_data.csv"
file_path_2 <- "../../outputs/data/cleaned_data.csv"

raw_data <- read_csv(file_path_0, show_col_types = FALSE)
filtered_data <- read_csv(file_path_1, show_col_types = FALSE)
cleaned_data <- read_csv(file_path_2, show_col_types = FALSE)
```

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-causes
#| tbl-cap: top 8 major causes in 2019

#### check top 8 major causes in 2019 ####
cleaned_data |>
  filter(
    calendar_year == 2019,
    ranking <= 8
  ) |>
  mutate(total_deaths = format(total_deaths, big.mark = ",")) |>
  kable(
    col.names = c("Year", "Cause", "Ranking", "Deaths", "Years"),
    align = c("l", "r", "r", "r", "r"),
    digits = 0, booktabs = TRUE, linesep = ""
  )

@@

```{r}
#| include: false
